Foraging: The Triumphant Return

### 2022-05-09 manuscript.tex

>>>>

We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnoteP{Full details of the analysis can be found in the supplementary materials}.

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection. Each line represents a different participant.  (\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates. The box shows the extent of the stimulus.}
\label{fig:qjep_init_sel_mdl}
\end{figure}
